A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.

### 2022-03-05 tex/manuscript.tex
Edit introdu nullcline description

\documentclass[utf8, draft]{frontiersFPHY} % for Physics and Applied Maths
% \documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{physics}
\usepackage{bm}
\usepackage{subfiles}

@@

@@

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Mark Olenik}

@@

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

@@

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.  In
  the inhibitory half-centre central pattern generators involved in locomotion, synaptic
  depression is believed to act as a burst termination mechanism, allowing networks to
  generate anti-phase bursting patterns of varying periods.  To better understand burst
  generation in these central patter generators, we study a minimal network of two neurons
  coupled through depressing synapses.  Depending on the strength of the synaptic
  conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase
  bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions
  increasing with the strength of the synaptic conductance.  Relying on the timescale
  disparity in the model, we reduce the eight-dimensional network equations to a
  fully-explicit scalar Poincaré burst map.  This map tracks the state of synaptic
  depression from one burst to the next and captures the complex bursting dynamics of the
  network.  Fixed points of this map are associated with stable burst solutions of the
  full network model, and are created through fold bifurcations of maps.  We derive
  conditions that describe period-increment bifurcations between stable $n-n$ and
  $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full
  network model and allow the study of parameter sensitivity for rhythm generation.

@@

\section{Introduction}
\section{Materials and Methods}
\subfile{sections/methods.tex}

\section{Results}
\subfile{sections/results.tex}

\section{Discussion}
\subfile{sections/discussion.tex}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-uncoupled.pdf}
  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$ is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/depression-traces.pdf}
  \caption{Solution profiles of a $4-4$ burst. $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange). $\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/burst-sols.pdf}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable solutions. Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase. During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-coupled.pdf}
  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line). $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions. Here the release condition is briefly satisfied after the first spike of cell 1. This does not cause firing of cell 2, which only occurs after the second spike of cell 1. $\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
    ~\label{fig:release-delay}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/free-quiet.pdf}
  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution. $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).  The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$. Each continuous branch is associated with a stable $n-n$ burst solution. Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/FQ-map.pdf}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/Pn-map.pdf}
  \caption{Map $\Pi_{n}:d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/folds.pdf}
  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$. $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

@@

>>>>

\documentclass[utf8, draft]{frontiersFPHY} % for Physics and Applied Maths
% \documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{physics}
\usepackage{cases}
\usepackage{bm}
% This should make nicer typesetting and lead to feaver underfull/overfull box errors
\usepackage{microtype}

@@

% Define terms for "free"/"quiet"
\newcommand{\free}{free}
\newcommand{\quiet}{suppressed}

@@

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
\def\Authors{Mark Olenik\,\(^{1,*}\), and Conor Houghton\,\(^{2}\)}
\def\Address{\(^{1}\)School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
\(^{2}\)School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
\def\corrAuthor{Mark Olenik}

@@

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.

@@

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric \(n-n\) anti-phase bursts, where neurons fire \(n\) spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  We derive conditions that describe period-increment bifurcations between stable \(n-n\) and \((n+1)-(n+1)\) bursts, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

@@

\input{sections/introduction}
\input{sections/methods}
\input{sections/results}
\input{sections/discussion}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-uncoupled.pdf}
  \caption{Periodic solution of relaxation-oscillator model neuron. \(\bm{\mathrm{(A)}}\)
    Projection of limit cycle onto (\(v,w\))-phase plane with \(v\)-nullcline (blue,
    \(v_\infty\)) and \(w\)-nullcline (orange, \(w_\infty\)). Unstable fixed point \(p_{f}\)
    is indicated by an orange dot. \(\bm{\mathrm{(B)}}\) Corresponding voltage trace
    \(v(t)\) of an action potential.~\label{fig:nullclines}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/depression-traces.pdf}
  \caption{Solution profiles of a \(4-4\) burst. \(\bm{\mathrm{(A)}}\) Membrane potentials
    of cell 1 (\(v_{1}\), blue), and cell 2 (\(v_{2}\), orange). \(\bm{\mathrm{(B)}}\)
    Synaptic variables \(d_{1}\) (blue) and \(s_{1}\) (grey) of cell
    1.~\label{fig:depression-traces}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/burst-sols.pdf}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing
    values of the coupling strength \(\gbar\) (increasing top to
    bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable \(n-n\) solutions for
    increasing coupling strength \(\gbar\). \(\bm{\mathrm{(A)}}\) Period of stable
    solutions. Dashed lines show the interval between the \(5-5\) and the suppressed
    solutions, where higher period \(n-n\) solutions occur on increasingly smaller intervals
    of \(\gbar\). \(\bm{\mathrm{(B)}}\) \(ISI\)s corresponding to \(n-n\) solutions in
    \(\mathrm{(A)}\). Long \(ISI\)s are associated with the quiet phase of a burst, short
    \(ISI\)s with the free phase. During the free phase, \(ISI\)s are of approximately
    constant duration \(T\).\label{fig:bif-diagram}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-coupled.pdf}
  \caption{Nullclines \(v_{\infty}\) (blue) and \(w_{\infty}\) (orange) in the
  \((v,w\))-phase plane for different values of the total synaptic conductance \(\gbar
  s\). For small \(\gbar s < g^{\star}\), fixed point \(p_{f}\) is unstable (orange
  point). Larger values \(\gbar s\) move \(v_{\infty}\) down in the \((v,w)\)-plane until
  \(p_{f}\) changes stability (half orange,  half blue point) at some critical total
  conductance value \(\gbar s = g^{\star}\), and becomes stable (blue point) for
  \(\gbar>g^{\star}\).~\label{fig:nullclines-coupled}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying \(\gbar\). Each of
    the three branches (A, B, C) also shows the timecourse of the total synaptic
    conductance \(\gbar s\) of a sample stable solution of both cells (blue and orange),
    as well as the release conductance \(g^{\star}\) (dashed green line).
    \(\bm{\mathrm{(A)}}\) Branch corresponding to the \(1-1\) solution. Here the quiet
    cell only spikes after a significant release delay. \(\bm{\mathrm{(B)}}\) Branch with
    a long release delay associated with a subset of \(2-2\) solutions. Here the release
    condition is briefly satisfied after the first spike of cell 1. This does not cause
    firing of cell 2, which only occurs after the second spike of cell 1.
    \(\bm{\mathrm{(C)}}\) Branch with \(n-n\) solutions  where release delay is
    approximately zero and the release condition is sufficient for firing of cell 2.
    ~\label{fig:release-delay}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/free-quiet.pdf}
  \caption{Schematic diagram of the free and quiet phases for a \(3-3\) solution.
    \(\bm{\mathrm{(A)}}\) Membrane potentials of cell 1 (\(v_{1}\)) and cell 2 (\(v_{2}\)).
    The grey patches depict inter-burst-intervals \(\delt\). \(\bm{\mathrm{(B)}}\) Total
    synaptic conductance of cell 1 (\(\gbar s_1\)) as it crosses the release conductance
    \(g^{\star}\). \(\bm{\mathrm{(C)}}\) Solution \(d_1(t)\) of depression variable of cell
    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of \(\delt\) for varying \(\gbar\).
    Each continuous branch is associated with a stable \(n-n\) burst solution. Increasing
    \(\gbar\) increases \(\Delta t\) until the solutions bifurcate at \(\Delta t\approx
    T\).~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/FQ-map.pdf}
  \caption{Maps \(F_n\) \(\bm{\mathrm{(A)}}\) and \(Q_n\) \(\bm{\mathrm{(B)}}\) for
  \(\gbar=0.6\) \(\si{mS/cm^{2}}\) and \(n=1,2,3,4\). Curves \(F_n\) intersect at
  \(d_{s}\) which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/Pn-map.pdf}
  \caption{Map \(\Pi_{n}:d^{\star}\). \(\bm{\mathrm{(A)}}\) \(\Pi_{n}\) for \(n=1,2,3,4\)
  at \(\gbar=0.6\) \(\si{mS/cm^{2}}\). \(\bm{\mathrm{(B)}}\) \(\Pi_{2}\) with \(n=2\) for
  varying \(\gbar \approx 0.01, 0.034, 0.3\) \(\si{mS/cm^{2}}\). The identity function is
  illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/folds.pdf}
  \caption{\(\bm{\mathrm{(A)}}\) Fold bifurcation diagrams of stable (continuous curves)
    and unstable (dotted curves) fixed points of \(\Pi_{n}\) for varying \(n\).
    \(\bm{\mathrm{(B)}}\) Cycle periods computed from stable fixed points (blue), and the
    corresponding solution period from numerical integration of the system of ODEs
    (orange).~\label{fig:folds}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable \(n-n\) solutions computed analytically from
    fixed points of \(\Pi_n\) and plotted on the respective intervals of \(\gbar\in
    \big[\gbar_+(n),\gbar_-(n)\big]\) (blue), and computed from numerical integrations of
    the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-03-05 tex/sections/discussion.tex
Edit introdu nullcline description

\documentclass[../manuscript.tex]{subfiles}
\graphicspath{{../figures/}}

\begin{document}

% PROBLEM SUMMARY
Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.

% MAIN RESULTS
To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
The results from our one-dimensional map match excellently with numerical simulation of the full network.
Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.

% FURTHER METHOD IDEAS
We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.

In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

% FLOW SYSTEM BIFURCATION
In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
% Should be possible to use averaging to reduce the system.

@@

\end{document}

>>>>

\section{Discussion}
% PROBLEM SUMMARY
Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming \citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}. In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}. Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.

% MAIN RESULTS
To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression. When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different \(n-n\) burst patterns. Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map \(\Pi_n\) of the slow depression variable \(d\). This map \(\Pi_n\) is a composition of two maps, \(F_n\) and \(Q_n\), that model the evolution of the depression during the free and quiet phases of \(n-n\) solutions respectively. Both \(F_n\) and \(Q_n\) maps are constructed by using the dynamics of single uncoupled neurons. Fixed points of \(\Pi_n\) are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable \(n-n\) burst solutions of the full two-cell system of ODEs. The results from our one-dimensional map match excellently with numerical simulation of the full network. Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.

% FURTHER METHOD IDEAS
We have studied \(n-n\) solutions assuming that the synaptic coupling \(\gbar \) between the two cells is symmetrical. However,~\citet{bose2011} have shown that asymmetrical coupling \((\gbar_1, \gbar_2)\) can result in network solutions of type \(m-n\), where one cell fires \(m\) spikes, while the other \(n\) spikes. It is conceivable that our map construction can be extended to also capture such \(m-n\) solutions. Remember, in the case of symmetrical coupling with \(n-n\) solutions, the timecourse of the depression variables \(d_{1}\) and \(d_{2}\) were in anti-phase, and it was therefore sufficient to track only one of the two variables. To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type \(m-n\), where the solutions of the depression variables \(d_1\) and \(d_2\) are not simply time-shifted versions of each other. To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map \(\Pi(d_1,d_2)\). While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}. Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons. As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses. In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.

In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}. It would therefore be interesting to study how varying the cell intrinsic firing period \(T\) could affect the network rhythm. While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying \(T\). Recall that \(T\) is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters. This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult. A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying \(T\) independently of other model parameters, and could be more fitting in this scenario.

% LIMITATION: SPIKE MAP
Our simulations of the network showed that \(n-n\) solutions lose robustness as their period is increased. That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength. We were able to replicate this finding by numerically finding the respective left and right borders of stable \(n-n\) branches of fixed points of \(\Pi_n\), and showing that the distance between these borders shrinks with \(n\). We have also noted the resemblance of our bifurcation diagram to one where such \(n-n\) branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}. It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}. Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity. The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods. In contrast, we rely on \(n\) different maps \(\Pi_n\) to describe the burst dynamics without explicitly capturing the period increment bifurcations. It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system. In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

% FLOW SYSTEM BIFURCATION
In addition to stable \(n-n\) solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable \(n-n\) solutions. While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points. However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
% Should be possible to use averaging to reduce the system.

@@
